---
title: "NEWS-XC95"
output: github_document
  #md_document:
   # variant: markdown_github
---

<!-- NEWS.md is generated from NEWS.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "NEWS-"
)
```

```{r, echo = FALSE}
cat(paste0("Last Update: ",Sys.time()))
```

Version history.

# Planned Updates

* Only bug fixes planned at this time.

* No vignettes planned at this time.

# v0.0.2.9003
2019-10-14

* HC05 calculation function.
* Add some formatting to data.R.
* Update DESCRIPTION.
* Add "Results" and "_test" directories to .gitignore and .Rbuildignore.

# v0.0.2.9002
2018-05-23

* tolerance
    + Updated parameters text.
    + Added Details section to describe output.
    + Added reference to maps package
    + No modifications of analysis.
* DESCRIPTION
    + Added maps to Imports.

# v0.0.2.9001
2018-04-23

* Add Travic_CI check to readme.

# v0.0.2.0000
2018-04-16

* wt.cdf
    + Replacement for fish.wt.cdf.
    + More generic and a few more inputs to make more adaptable.

# v0.0.1.9004
2018-04-13

* fish.wt.cdf, Example remove extra comment.
* wt.cdf
    + Updated version of fish.wt.cdf.
    + More flexibility with groups.
    + Added group names.
    + Defaulted all boolean parameters to TRUE.
    
# v0.0.1.9003
2018-04-12

* fish.wt.cdf, Example
    + Updated group WS_Area to WS_AREA to match example data.
    + Updated example function to include groups and xvar.
    + Updated example SampleID from FishInvertID to Station_Date.

# v0.0.1.9002
2017-04-25

* Update News.rd and remove an extra folder left from testing.  No modifications to code.

# v0.0.1.9001
2017-04-25

* Added area under the curve functions (auc.response() and auc.tolerance()) as independant functions.  Removed code from the other functions (taxon.response(), taxon.response.sort(), and tolerance()).

# v0.0.1.0000
2017-04-24

* Updated documentation to a whole number version and created a "release" on GitHub.

# v0.0.0.9006
2017-04-24

* Removed fish.gam().  It is designed for another purpose.

* fish.wt.cdf().  Was previously named weighted.fish.cdf().


# v0.0.0.9005
2017-04-18

* taxon.response().  Tweaked for example.  Added and documented data files (QC_Benthic.txt and Env_metrics.txt as species and envdata.all).  Added "mgcv::" to "gam()." and "Hmisc::" to "wtd.quantile" and "Ecdf".


# v0.0.0.9004
2017-04-14

* Revised comment strings in scripts so will properly outline in RStudio; curve.shape.R, fish.wt.cdf.R, taxon.response.R, taxaon.response.sort.R, and tolerance.R.  Also modified data prep files in raw data.

* tolerance().  Tweaked for example.  Added data files (tol.ss and tol.env.data).  Added "mgcv::" to "gam()." and "Hmisc::" to "wtd.quantile".  Created data from raw files and documented.

# v0.0.0.9003
2017-04-06

* taxon.response.sort().  Process raw data.  Add data files df1.rda and taxalist.rda. Add library mgcv reference for gam().  Updated data.R for df1 and taxalist.

* Added new function dir.check.add() to ensure output folders exist.

* DESCRIPTION.  Add mgcv to Imports.

# v0.0.0.9002
2017-04-05

* Rename package from InvertExtirp to XC95.  Update DESCRIPTION, NEWS, and README.

* Add data to use with examples.

* Added raw data for weightcdf().  Included script for creating the RDA files.

* Added documentation for the above data files (ss and bio.sample).

# v0.0.0.9001
2017-04-04

* Update the R files for readability, documentation, and dependant packages for the functions.  "tolerance_cov.R" requires the "reshape" package (update one call to reshape::cast and add to DESCRIPTION).

* Rename "tolerance_cov.R" to "tolerance.R" to match the function.

# v0.0.0.9000
2017-03-29

* Created GitHub repository.

* Added ReadME.RMD and NEWS.RMD

* 7 functions; curve.shape, fish.gam, fish.wt.cdf, taxon.response, taxon.response.sort, tolerance_cov, weightedcdf2.


